Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-16 paper/example.tex
Add new tex files, reformat agree section, and revise that text

A cyber-vulnerability analysis, however, identifies the potential of a supply chain attack through the AI route planner that is provided by a third-party vendor without source code.
The component is marked as \emph{untrusted} after the analysis, and its contract is modified by removing all guarantees on its outputs to reflect its untrusted status.
The AI output is now unconstrained in the assume-guarantee reasoning of AGREE and is able to generate any value on its output stream at anytime.
AGREE must consider all possible output streams from the AI in proving the correctness of the component implementation of the automated UAV route planning system.

@@

The AGREE analysis of the cyber-hardened implementation with the auto-generated high-assurance components is shown in \figref{fig:hardened}.
Here AGREE provides a proof certificate that the high-assurance components guarantee the correct behavior of the SW implementation in the presence of the untrusted AI route planner.

>>>>

A cyber-vulnerability analysis, however, identifies the potential of a supply chain attack through the AI route planner that is provided by a third-party vendor without source code.
The component is marked as \emph{untrusted} after the analysis, and its contract is modified by removing all guarantees on its outputs to reflect its untrusted status.
The AI output is now unconstrained in the assume-guarantee reasoning of AGREE and is able to generate any value on its output stream at anytime.

@@

The AGREE analysis of the cyber-hardened implementation with the auto-generated high-assurance components is shown in \figref{fig:hardened-certificate}.
Here AGREE provides a proof certificate that the high-assurance components guarantee the correct behavior of the SW implementation in the presence of the untrusted AI route planner.
Having passed AGREE verification, the high-assurance components are ready to be synthesized.

### 2022-03-16 paper/paper.tex
Add AGREE verification conditions
Revise example section
Revise the AGREE semantics and reorder section
Add new tex files, reformat agree section, and revise that text

\lstdefinestyle{agree}
{frame=none,
  basicstyle=\ttfamily,
  language=ML,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  numbers=none,
  numberstyle=\tiny\color{gray},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=true,
  tabsize=2,
  linewidth=2\linewidth,
  morekeywords={eq, bool, guarantee, assume, true, false, pre, not, and, or, property, const, Historically, Since, Once, event}
}

\hyphenation{op-tical net-works semi-conduc-tor}

@@

\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Sec.~\ref{#1}}

@@

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Reformat text to put single sentence on each line.}
  \item Move example to its own repository, archive, and give the DOI and URL for the example.
  \item \sout{Update AGREE certificates with new model}
  \item Separate example into separate files for initial design, cyber-components and tests, hardened design, and seL4 process design.
  \item \sout{Make clear the initial properties for the assumed correct model:}
    \begin{compactitem}
      \item \sout{Assume at the system level that a new automation request is not sent unless the prior request, if any, is acknowledged}
      \item \sout{Assume at all levels input messages are well-formed}
      \item \sout{Guarantee at all levels that waypoint outputs coincide with air vehicle location messages}
      \item \sout{Guarantee that a start from the waypoint manager coincides with an automation response}
      \item \sout{Guarantee for all trusted components that outputs are well-formed}
    \end{compactitem}
\end{compactitem}

\section{AGREE Contract Specification} \label{sec:agree}
\input{agree}

@@

\section{AGREE Semantics for Component Synthesis}
\input{semantics}

>>>>

\lstdefinestyle{agree}
{frame=none,
  basicstyle=\ttfamily,
  language=ML,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  numbers=none,
  numberstyle=\tiny\color{gray},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=true,
  tabsize=2,
  linewidth=2\linewidth,
  morecomment=[l]{--},
  morekeywords={eq, bool, guarantee, assume, true, false, pre, not, and, or, property, const, Historically, Since, Once, event}
}

\hyphenation{op-tical net-works semi-conduc-tor Cake-ML}

@@

\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Sec.~\ref{#1}}
\newcommand{\lineref}[1]{Line~\ref{#1}}
\newcommand{\linesref}[2]{Lines~\ref{#1}-\ref{#2}}

@@

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Reformat text to put single sentence on each line.}
  \item Move example to its own repository, archive, and give the DOI and URL for the example.
  \item \sout{Update AGREE certificates with new model}
  \item Separate example into separate files for initial design, cyber-components and tests, hardened design, and seL4 process design.
  \item \sout{Make clear the initial properties for the assumed correct model:}
    \begin{compactitem}
      \item \sout{Assume at the system level that a new automation request is not sent unless the prior request, if any, is acknowledged}
      \item \sout{Assume at all levels input messages are well-formed}
      \item \sout{Guarantee at all levels that waypoint outputs coincide with air vehicle location messages}
      \item \sout{Guarantee that a start from the waypoint manager coincides with an automation response}
      \item \sout{Guarantee for all trusted components that outputs are well-formed}
    \end{compactitem}
  \item Add citations to last paragraph for scheduled AGREE and HAMR.
\end{compactitem}

\section{Assume-Guarantee Reasoning in AGREE}
\label{sec:agree}
\input{agree}

@@

\section{AGREE Semantics for Component Synthesis}
\label{sec:semantics}
\input{semantics}
